Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2022-12-05 src/tex/results.tex
more referee responses done

We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin, and redshift distributions of 
binary black holes (BBHs) given a catalog of gravitational wave observations. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist,GWTC3DATA}. Since it was concluded to be an outlier of the rest of 
the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer population properties. Our study provides the first comprehensive 
data-driven investigation of the BBH mass, spin, and redshift distributions, uncovering new insights and corroborating those found with other methods. 
We start with our inference of the mass distribution.

>>>>

We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin, and redshift distributions of 
binary black holes (BBHs) given a catalog of gravitational wave observations. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist,GWTC3DATA}. Since it was concluded to be an outlier of the rest of 
the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer population properties. 
\NewChange{Following what was done in \citet{o3b_astro_dist}, for events included in GWTC-1 \citep{GWTC1}, we use the published samples that equally weight samples from analyses with the \textsc{IMRPhenomPv2} \citep{1308.3271} and \textsc{SEOBNRv3} \citep{1307.6232,1311.2544} waveforms. For the events from GWTC-2 \citep{gwtc2}, we use samples that equally weight all available analyses using higher-order mode waveforms (\textsc{PrecessingIMRPHM}). Finally, for new events reported in GWTC-2.1 and GWTC-3 \citep{2108.01045,GWTC3}, we use combined samples, equally weighted, from analyses with the \textsc{IMRPhenomXPHM} \citep{2004.06503} and the \textsc{SEOBNRv4PHM} \citep{2004.09442} waveform models.}
Our study provides the first comprehensive 
data-driven investigation, simultaneously inferring all the BBH population distributions (i.e. mass, spin, and redshift), uncovering new insights and corroborating those found with other methods. 
We start with our inference of the mass distribution.
